---
title: "AE-portfolio-tidytuesday-tutorial"
author: "Alex Connolly and Elayna Seago"
date: "3/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#In this tutorial we will walk you through downloading and using data sets from tidy tuesday

#Step 1: go to the tidy tuesday website, scroll down, and find the TBI data (in March of 2020)

#Step 2: Create your own repository in github and open it using new project/version control/github (or however you make your repositories)

#Step 3: Read the files into tidy tuesday. You can do this by looking at the code template there, or just by using read_csv. See below for an example of using the template put on tidy tuesday

```{r read-in-data}
tbi_age <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_age.csv')
tbi_year <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_year.csv')
tbi_military <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-24/tbi_military.csv')
```
```{r load-libraries}
library(tidyverse)
```


#run all and knit-make sure everything is working!

```{r lets-do-activities}
tbi_age %>%
  ggplot(mapping = aes(x = age_group, fill = type)) + geom_bar()
```

